### 2015-05-15 whoop.tex
fix
added page in book

To make our analysis scale while maintaining precision, and to support recursion, we use the Houdini algorithm~\cite{flanagan2001houdini} to automatically compute summaries (pre- and post-conditions and loop invariants).  Given a pool of \emph{candidate} pre-conditions, post-conditions, and loop invariants, Houdini repeatedly attempts to verify each procedure.  Initially, the entire candidate pool is considered.  If verification fails due to an incorrect candidate, this candidate is discarded.  The process repeats until a fixpoint is reached.  The (possibly empty) set of remaining candidates have been proven to hold, and can used to summarize calls and loops during further program analysis.

@@

Another limitation of \whoop is that it is unable to verify drivers designed to be accessed by only a single process at a time. This \emph{single-open device}~\cite{corbet2005linux} mode can be enforced by atomically testing (at the beginning of an entry point) a flag that indicates device availability: if the flag is set to true, then the checking entry point executes, else it blocks. Because \whoop performs pair-wise analysis, it over-approximates this flag, and thus can falsely report a pair as racy. However,~\cite{corbet2005linux} advises against serializing drivers in this way, as it hinders user ingenuity (e.g.\ a user might expect that a device can be accessed concurrently for performance).

>>>>

To make our analysis scale while maintaining precision, and to support recursion, we use the Houdini algorithm~\cite{flanagan2001houdini} to automatically compute summaries (pre- and post-conditions and loop invariants).  Given a pool of \emph{candidate} pre-conditions, post-conditions, and loop invariants, Houdini repeatedly attempts to verify each procedure.  Initially, the entire candidate pool is considered.  If verification fails due to an incorrect candidate, this candidate is discarded.  The process repeats until a fixpoint is reached.  The (possibly empty) set of remaining candidates has been proven to hold, and can used to summarize calls and loops during further program analysis.

@@

Another limitation of \whoop is that it is unable to verify drivers designed to be accessed by only a single process at a time. This \emph{single-open device}~\cite[p.\ 173]{corbet2005linux} mode can be enforced by atomically testing (at the beginning of an entry point) a flag that indicates device availability: if the flag is set to true, then the checking entry point executes, else it blocks. Because \whoop performs pair-wise analysis, it over-approximates this flag, and thus can falsely report a pair as racy. However,~\cite{corbet2005linux} advises against serializing drivers in this way, as it hinders user ingenuity (e.g.\ a user might expect that a device can be accessed concurrently for performance).
